First steps towards a formalization of Forcing \\ Revisions made to the paper

### 2018-11-19 LSFA/cover_letter.tex
spell check

The section on ``Names'' includes a thorough discussion on recursive
definitions in Isabelle/ZF and two new applications. The first is the proof
that the generic extension $M[G]$ is a transitive set; and the second
is that thegeneric filter $G$ belongs to $M[G]$, a fundamental result
that was missing from the previous two versions.

>>>>

The section on ``Names'' includes a thorough discussion on recursive
definitions in Isabelle/ZF and two new applications. The first is the proof
that the generic extension $M[G]$ is a transitive set; and the second
is that the generic filter $G$ belongs to $M[G]$, a fundamental result
that was missing from the previous two versions.
